---
title: "Adjumani ECHO Assessment - Field Data Collection Tracker"
author: "REACH"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_file = paste0(dirname(inputFile), '/adjumani_echo_field_data_collection_tracker_', format(Sys.Date(), '%Y_%m_%d'),'.html')) })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)

# read packages
library(tidyverse)
library(lubridate)
library(glue)
library(leaflet)

# df_logical_check_description <- readxl::read_excel("inputs/aba_logical_checks_overview.xlsx") %>%
#     janitor::clean_names() %>%
#     select(check_number, check_description) %>%
#     mutate(check_number = as.character(check_number))

df_refugee_samples <- readr::read_csv("../inputs/Refugee_adjumani_aba_survey_samples_definition.csv")

df_for_colnames <- df_refugee_samples %>% 
    mutate(across(where(is.character), str_to_lower)) %>%
    rename(meta_division_name = subcounty_division_settlement) %>% 
    mutate(meta_division_name = meta_division_name,
           meta_division_name = str_replace_all(string = meta_division_name, pattern = " ", replacement = "_"),
           meta_village_name = str_to_lower(village_cell),
           meta_village_name = str_replace_all(string = meta_village_name, pattern = " ", replacement = "_")
    ) %>% 
    select(meta_division_name, meta_village_name) %>% 
    unique()

df_village_name_samples_required <- df_refugee_samples %>% 
    rename(meta_village_name = village_cell) %>% 
    select(meta_village_name, sample_size) %>% 
    mutate(meta_village_name = str_to_lower(meta_village_name),
           meta_village_name = str_replace_all(string = meta_village_name, pattern = " ", replacement = "_"))

df_host_samples <- readr::read_csv("../inputs/Host_community_adjumani_aba_survey_samples_definition.csv")

df_for_host_colnames <- df_host_samples %>% 
    mutate(across(where(is.character), str_to_lower)) %>% 
    rename(meta_division_name = subcounty_division_settlement) %>%
    mutate(meta_division_name = meta_division_name,
           meta_division_name = str_replace_all(string = meta_division_name, pattern = " ", replacement = "_"),
           meta_village_name = str_to_lower(village_cell),
           meta_village_name = str_replace_all(string = meta_village_name, pattern = " ", replacement = "_")
    ) %>% 
    select(meta_division_name, meta_village_name) %>% 
    unique()

df_host_samples_required <- df_host_samples %>% 
    rename(meta_village_name =  village_cell ) %>%
    select(meta_village_name, sample_size) %>% 
    mutate(meta_village_name = str_to_lower(meta_village_name),
           meta_village_name = str_replace_all(string = meta_village_name, pattern = " ", replacement = "_")
    )

df_tool_data <- readxl::read_excel("../inputs/UGA2401_Adjumani_ECHO_data.xlsx") %>%
    mutate(uuid = `_uuid`,
           start_date = as_date(start),
           start = as_datetime(start),
           end = as_datetime(end),
           meta_village_name = as.character(meta_village_name),
           latitude = as.numeric(`_geopoint_latitude`),
           longitude = as.numeric(`_geopoint_longitude`))

# days that contain data
df_days_for_data_collection <- df_tool_data %>% select(start_date) %>% unique() %>% arrange(start_date) %>% pull()

df_data_support_cl_log <- df_tool_data %>% 
    select(uuid, status, meta_division_name, point_number, meta_village_name, latitude,	longitude )

# cleaning log handling
df_cl_log <- read_csv(file = "../inputs/combined_checks_adjumani_echo_assessment.csv") %>% 
    rename(village_name = meta_village_name) %>% 
    # filter(!str_detect(string = point_number, pattern = fixed('test', ignore_case = TRUE))) %>% 
    mutate(change_type = ifelse(is.na(change_type), "no_action", change_type)) %>% 
    left_join(df_data_support_cl_log, by = "uuid")

# change_response logs that affect stats in the data collection progress
cl_log_change_response <- df_cl_log %>% 
    filter(change_type == "change_response", 
           !is.na(new_value),
           # reviewed == 1, 
           change_type != "no_action",
           !str_detect(string = question, "\\/")
    ) %>% 
    select(uuid, question, new_value)

# updated tool data
df_updated_tool_data <- df_tool_data

# get uuids from cleaning log
uuids_chg_response <- cl_log_change_response %>% pull(uuid) %>% unique()

for (current_uuid in uuids_chg_response) {
    current_uuid_data <- cl_log_change_response %>% 
        filter(uuid == current_uuid) %>% 
        mutate(new_value = ifelse(question == "enumerator_id", as.numeric(new_value), new_value)) %>% 
        pivot_wider(names_from = "question", values_from = "new_value", uuid)
    print(current_uuid_data)
    # process current updates
    df_current_updated <- df_updated_tool_data %>% 
        rows_update(y = current_uuid_data, by = "uuid")
    # update the parent dataset with current updates
    df_updated_tool_data <- df_current_updated
}

# enumerator performance data
df_enum_performance <- df_updated_tool_data %>% 
    mutate(int.survey_time_interval = lubridate::time_length(end - start, unit = "min"),
           int.survey_time_interval = ceiling(int.survey_time_interval))


# functions for changing some options in the table
dt_set_options<- function(x){
  DT::datatable(x,
                options = list(
                  autoWidth=F,
                  dom= 't',
                  list(list(width = '20%', targets = list(1,2,3,4,5)))
                )
  )
}

dt_with_modified_options <- function(x){
  DT::datatable(x,
                rownames = FALSE,
                options = list(
                  columnDefs = list(list(className = 'dt-center', targets = list(1,2,3,4,5))),
                  pageLength = 20,
                  initComplete = JS(
                    "function(settings, json) {",
                    "$(this.api().table().header()).css({'background-color': '#333', 'color': '#fff'});",
                    "}")
                )
  )
}

dt_options_fewcols <- function(x){
  DT::datatable(x,
                rownames = FALSE,
                options = list(
                  pageLength = 20,
                  initComplete = JS(
                    "function(settings, json) {",
                    "$(this.api().table().header()).css({'background-color': '#333', 'color': '#fff'});",
                    "}")
                )
  )
}

dt_enum_performance_options <- function(x){
  DT::datatable(x,
                rownames = FALSE,
                filter = 'top',
                options = list(
                  columnDefs = list(list(className = 'dt-center', targets = list(1,2))),
                  pageLength = 50,
                  initComplete = JS(
                    "function(settings, json) {",
                    "$(this.api().table().header()).css({'background-color': '#333', 'color': '#fff'});",
                    "}"),
                  order = list(list(1, 'desc'), list(0, 'asc'), list(3, 'desc'))
                )
  )
}
```

## Summary on the surveys done

>There are **`r nrow(df_updated_tool_data)`** total number of surveys done as of **`r df_days_for_data_collection[length(df_days_for_data_collection)]`**.

>The average survey time for all the data is: **`r round(mean(df_enum_performance$int.survey_time_interval), 0)`** Minutes

### Refugees  **`r df_updated_tool_data %>% filter(status == "refugee") %>% nrow()`** surveys

```{r, echo = FALSE}
df_refugee_samp_per_village_name <- df_village_name_samples_required %>% 
    group_by(meta_village_name) %>% 
    summarise(required_samples = sum(sample_size, na.rm = TRUE))
              # samples_without_buffer = sum(sample_size_without_buffer, na.rm = TRUE))

df_cl_surveys_for_deletion <- df_cl_log %>% 
    filter(status == "refugee",  change_type == "remove_survey", 
           change_type != "no_action") %>%
    group_by(meta_village_name) %>% 
    distinct(uuid) %>%
    summarise(surveys_for_deletion = n())

df_updated_tool_data %>% 
    filter(status == "refugee") %>% 
    group_by(meta_division_name, meta_village_name) %>% 
    summarise(surveys_completed = n()) %>% 
    arrange(meta_division_name) %>% 
    right_join(df_refugee_samp_per_village_name, by = "meta_village_name") %>% 
    left_join(df_cl_surveys_for_deletion, by = "meta_village_name") %>% 
    mutate(surveys_completed = ifelse(is.na(surveys_completed), 0, surveys_completed),
           surveys_for_deletion = ifelse(is.na(surveys_for_deletion), 0, surveys_for_deletion),
           int.surveys_and_deletion = surveys_completed - surveys_for_deletion,
           remaining_surveys = required_samples - int.surveys_and_deletion) %>%
           # remaining_surveys_with_buffer = samples_with_buffer - int.surveys_and_deletion,
           # remaining_surveys_no_buffer = samples_without_buffer - int.surveys_and_deletion ) %>% 
    left_join(df_for_colnames, by = "meta_village_name") %>% 
    rename(meta_division_name = meta_division_name.x) %>%
    mutate(meta_division_name = meta_division_name.y) %>%
    select(-c(int.surveys_and_deletion, meta_division_name.y))  %>% 
  dt_with_modified_options()
```

### Host community: **`r df_updated_tool_data %>% filter(status == "host_community") %>% nrow()`** surveys

```{r, echo = FALSE}
df_host_samp_per_sub_county <- df_host_samples_required %>% 
    group_by(meta_village_name) %>% 
    summarise(required_samples = sum(sample_size, na.rm = TRUE))
              # samples_without_buffer = sum(sample_size_without_buffer, na.rm = TRUE))

df_cl_surveys_for_deletion <- df_cl_log %>% 
    filter(status == "host_community", change_type == "remove_survey", change_type != "no_action") %>%
    group_by(meta_village_name) %>% 
    distinct(uuid) %>%
    summarise(surveys_for_deletion = n())

df_updated_tool_data %>% 
    filter(status == "host_community") %>% 
    group_by(meta_division_name, meta_village_name) %>% 
    summarise(surveys_completed = n()) %>% 
    arrange(meta_division_name) %>% 
    right_join(df_host_samp_per_sub_county, by = "meta_village_name") %>% 
    left_join(df_cl_surveys_for_deletion, by = "meta_village_name") %>% 
    mutate(surveys_completed = ifelse(is.na(surveys_completed), 0, surveys_completed),
           surveys_for_deletion = ifelse(is.na(surveys_for_deletion), 0, surveys_for_deletion),
           int.surveys_and_deletion = surveys_completed - surveys_for_deletion,
           remaining_surveys = required_samples - int.surveys_and_deletion) %>% 
           # remaining_surveys_with_buffer = samples_with_buffer - int.surveys_and_deletion,
           # remaining_surveys_no_buffer = samples_without_buffer - int.surveys_and_deletion) %>% 
    left_join(df_for_host_colnames, by = "meta_village_name") %>% 
    rename(meta_division_name = meta_division_name.x) %>%
    mutate(meta_division_name = meta_division_name.y) %>%
    select(-c(int.surveys_and_deletion, meta_division_name.y)) %>% 
  dt_with_modified_options()

```
### Gender disaggregation by respondent status
# Refugees
```{r, echo = FALSE}
df_gender_disaggregation_refugee <-  df_tool_data %>% 
    filter(status == "refugee") %>% 
    group_by(meta_village_name) %>% 
    count(meta_respondent_gender) %>% 
    pivot_wider(names_from = meta_respondent_gender,
                values_from = n) %>% 
    replace(is.na(.),0) %>% 
    mutate(percentage_male = male/sum(female, male)*100,
           percentage_female = female/sum(female, male)*100) %>% 
    mutate(across(where(is.numeric), round, 0)) %>% 
    rename_with(~str_replace(string = .x, pattern = "percentage_female", replacement = "female(%)")) %>% 
    rename_with(~str_replace( string = .x, pattern = "percentage_male", replacement = "male(%)")) 

df_gender_disaggregation_refugee %>% 
    DT::datatable()
```
# Host Community
```{r, echo = FALSE}
df_gender_disaggregation_host <-  df_tool_data %>% 
    filter(status == "host_community") %>% 
    group_by(meta_village_name) %>% 
    count(meta_respondent_gender) %>% 
    pivot_wider(names_from = meta_respondent_gender,
                 values_from = n) %>% 
    replace(is.na(.),0) %>% 
    mutate(percentage_male = male/sum(female, male)*100, 
           percentage_female = female/sum(female, male)*100) %>% 
    mutate(across(where(is.numeric), round, 0)) %>%  
    rename_with(~str_replace(string = .x, pattern = "percentage_female", replacement = "female(%)")) %>% 
    rename_with(~str_replace( string = .x, pattern = "percentage_male", replacement = "male(%)")) 

df_gender_disaggregation_host %>% 
    DT::datatable()


```

### Daily enumerator performance

```{r, echo = FALSE}

df_enum_performance %>% 
  group_by(meta_division_name, start_date, enumerator_id) %>% 
  summarise(number_of_interviews_done = n(), `average_survey_time(minutes)` = round(mean(int.survey_time_interval, na.rm = TRUE), 0)) %>% 
  dt_enum_performance_options()

```

## Looking into the cleaning log

### Number of issues by enumerator

```{r, echo = FALSE}
df_cl_log %>% 
    group_by(meta_division_name, enumerator_id) %>% 
    summarise(number_of_issues_by_enumerator_id = n()) %>% 
  dt_options_fewcols()
  
```

### Enumerators with surveys for deletion
```{r, echo = FALSE}
df_cl_log %>%
    filter(change_type == "remove_survey", change_type != "no_action") %>% 
    group_by(meta_village_name, enumerator_id) %>%
    summarise(number_of_surveys_for_deletion_by_enumerator = n()) %>% 
  dt_options_fewcols()

```
<!-- ### Map of surveys for deletion -->

<!-- ```{r, echo = FALSE, out.width="100%"} -->
<!-- # popup -->
<!-- labels_pts <- ~sprintf( -->
<!--   "<strong>Status and Name: %s</strong><br/> -->
<!--       Point Number :  <strong>%s</strong><br/> -->
<!--       Issue :  <strong>%s</strong><br/> -->
<!--       Enumerator ID :  <strong>%s</strong>", -->
<!--   int.status, point_number, issue, enumerator_id -->
<!-- ) %>% -->
<!--   lapply(htmltools::HTML) -->

<!-- df_cl_log %>% -->
<!--   filter(change_type == "remove_survey", change_type != "no_action") %>% -->
<!--   group_by(uuid, status, meta_division_name, meta_village_name, latitude, longitude) %>% -->
<!--   summarise(today = paste(today, collapse = " : "), -->
<!--             enumerator_id = paste(enumerator_id, collapse = " : "), -->
<!--             meta_division_name = paste(meta_division_name, collapse = " : "), -->
<!--             point_number = paste(point_number, collapse = " : "), -->
<!--             change_type = paste(change_type, collapse = " : "), -->
<!--             question = paste(question, collapse = " : "), -->
<!--             old_value = paste(old_value, collapse = " : "), -->
<!--             new_value = paste(new_value, collapse = " : "), -->
<!--             issue = paste(issue, collapse = " : ") -->
<!--   ) %>% -->
<!--   unique() %>% -->
<!--   mutate(int.status = ifelse(status == "refugee", -->
<!--                              glue("{status}_{meta_village_name}"), glue("{status}_{meta_division_name}"))) %>% -->
<!--   leaflet() %>% -->
<!--   addTiles() %>% -->
<!--   addCircleMarkers(~longitude, -->
<!--                    ~latitude, -->
<!--                    popup = labels_pts, -->
<!--                    radius = 10, -->
<!--                    color = "red", -->
<!--                    stroke = FALSE, fillOpacity = 0.9, -->
<!--                    label = labels_pts, -->
<!--                    clusterOptions = markerClusterOptions()) -->
<!-- ``` -->
